\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\begin{center}
\textbf{Use Case I3S5:  Detailed Description}
\end{center}
Use Case Name:  Manage Mission Data\\
Scenario:  S5 Save Mission Data\\
Brief Description:  With the System Running, the User requests to
save the current data to the current Database. The user also saves off
the data in text format by entering the directory and file name where
to save the data (usually in .cvs format).\\
Actors:  User, Database Administrator\\
Related Use Cases:  none\\\\
Stakeholders:  Users who want to archive the data.  Database
Administrators who want to maintain and safely archive the Mission
data.\\\\
Precondtions:  The system is running.  Mission Data is loaded onto the
System:  See Use Cases \textbf{I3S1-I3S4}, View Temperature Data,
View Humidity Data, View Heat Index Data, View Dew Point Data. The
Data Base is set up, with the Data Base Server running.\\\\
Postconditions:  The Mission Data is saved to the appropriate CSV file
and/or to the approriate Data Base.\\\\
\textbf{Flow of Events}\\\\
\begin{tabular}{|l|l|}\hline
\textbf{User} & \textbf{System}\\\hline
1.  Request to Save the Mission Data & \\\hline
& 2.  Presents the dialog box to save\\
& the data in CSV format\\\hline
3.  Decides if to save the data in & \\
CSV format and where entering the & \\
Data as appropriate & \\\hline
& 4. Opens the CSV file and saves\\
& the data.\\\hline
& 5.  Appends the appropriate data to\\
& the Data Base:  Temperature, Humidity\\
& Dewpoint, Heat Index with the \\
& Appropriate Time and the Appropriate\\
& Units (Fahrenheit, Celsius, Kelvin)\\
& for the Temperature, Dewpoint, Heat\\
& Index\\\hline
& 6.  Sends the appropriate ``save" message\\
& to the User, indicating the data was\\
& saved to the appropriate CSV file (if\\
& the user requested) and to the appropriate\\
& Data Base\\\hline
\end{tabular}\\\\
\textbf{Exception Conditions}\\
2a, 4a, 5a.  If there is no data to save, then the system notifies the
user there is no data.\\\\
4b.  If there is an error in saving the CSV file, then the system
notifies the user of the problem.\\\\
5b.  If the data base is not open/loaded, then the system notifies the
user the data cannot be saved to the Database.\\\\
5c.  If there is a write error in appending the data to the Database,
then the System notifies the user of the write error, and the
inability of the Database to save/append the data.
\end{document}
