\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\begin{center}
\textbf{Use Case I3S3:  Detailed Description}
\end{center}
Use Case Name:  Manage Mission Data\\
Scenario: S3 View Dewpoint Data\\
Brief Description:  WIth the System Running, the User requests to view
the current Dewpoint Data (regardless if an IButton Mission is
running).\\
Actors:  User\\
Related Use Cases:\\Use Case I3S1: \textbf{View Temperature Data},\\
Use Case I3S2: \textbf{View Humidity Data}\\\\
Stakeholders:  Users who what to view the current Dewpoint Data from
the current IButton Mission.\\\\
Preconditions:  The System is running, the IButton device is connected
to the receptor or other reading device.  The IButton receptor or other
reading device is connected to the computer.\\\\
Postconditions:  The Dewpoint data is retrieved from the IButton and
presented to the User for display. (In either textual or graphical
form).\\\\
\textbf{Flow of Events}\\\\
\begin{tabular}{|l|l|}\hline
\textbf{User} & \textbf{System}\\\hline
1.  Request Dewpoint Data for & \\
viewing & \\\hline
& 2. Retrieves the current Temperature\\
& data.\\\hline
& 3. Retrieves the current Humidity\\
& data.\\\hline
& 4.  Calculates the current Dewpoint\\\hline
& 5.  Separates the Dewpoint data by\\
& Date.\\\hline
& 6.  Determines the Min/Max of the\\
& current Dewpoint data and the\\
& associated Date/Time\\\hline
& 7.  Presents the requested Dewpoint\\
& data to the User for viewing.\\\hline
8. Determines how to view the data &\\
(in \textbf{Text or Graphical} format) &\\
Makes the request to the System &\\\hline
& 9.  Presents the data in the requested\\
& format.\\\hline
\end{tabular}\\\\
\textbf{Exception Conditions}\\
1a.  If no iButton Device is connected to the network, then the system
indicates the error to the user with the reason (no iButton Attached).
\\\\
2a.  If the Temperature Data of the current mission cannot be
retrieved,
then the system indicates the error to the user with the reason (See
\textbf{Use Case I3S1, Exception Condition 2a}).\\\\
3a.  If the Humidity Data of the current mission cannot be retrieved,
then the system indicates the error to the user with the reason (See
\textbf{Use Case I3S2, Exception Condition 2a}).\\\\
4a.  If the System is not capable of calculating the Dewpoint data
(See \textbf{Exception Conditions 2a, 3a}), then the System
indicates the issue and the reason.\\\\
5a.  If the associated Date/Time of the requested Dewpoint data
is not retrievable, then the System indicates the error to the User
with the reason (\textit{One Wire Network Issues, One Wire Device
Issues, other forms of data retrieval exceptions}).
\end{document}